Follow-up Samples

### 2017-01-16 submission/manuscript_outline_20161024.Rmd
correct centering problem

---
title: ""
bibliography: reference.bib
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
  html_document: default
csl: microbiome.csl
fontsize: 12pt
geometry: margin=1.0in
---

# Differences in the Stool Microbiome Before and After Colorectal Cancer Treatment

```{r knitr_settings, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

```
\begin{center}  
\vspace{25mm}

Running Title: Human Microbiome and Colorectal Cancer

@@

Marc A Sze^1^, Nielson T Baxter^2^, Mack T Ruffin IV^3^, Mary AM Rogers^4^, and Patrick D Schloss^1^${^\dagger}$

@@

^1^Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI  
^2^Department of Internal Medicine, Division of Infectious Disease, University of Michigan, Ann Arbor, MI  
^3^Department of Family Medicine and Community Medicine, Penn State Hershey Medical Center, Hershey, PA  
^4^Department of Internal Medicine, University of Michigan, Ann Arbor, MI
\end{center}

>>>>

---
title: ""
bibliography: reference.bib
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
csl: microbiome.csl
fontsize: 12pt
geometry: margin=1.0in
---

# Differences in the Stool Microbiome Before and After Colorectal Cancer Treatment
```{r knitr_settings, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

```
\vspace{25mm}

\begin{center}
Running Title: Human Microbiome and Colorectal Cancer

@@

Marc A Sze${^1}$, Nielson T Baxter${^2}$, Mack T Ruffin IV${^3}$, Mary AM Rogers${^2}$, and Patrick D Schloss${^1}$${^\dagger}$

@@

$1$ Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI

$2$ Department of Internal Medicine, University of Michigan, Ann Arbor, MI

$3$ Department of Family Medicine and Community Medicine, Penn State Hershey Medical Center, Hershey, PA

\end{center}

### 2017-01-16 submission/manuscript_outline_20161024.tex
correct centering problem

\textbackslash{}begin\{center\}\\
\vspace{25mm}

Running Title: Human Microbiome and Colorectal Cancer

@@

Marc A Sze\textsuperscript{1}, Nielson T Baxter\textsuperscript{2}, Mack
T Ruffin IV\textsuperscript{3}, Mary AM Rogers\textsuperscript{4}, and
Patrick D Schloss\textsuperscript{1}\({^\dagger}\)

@@

\(\dagger\) To whom correspondence should be addressed:
\href{mailto:pschloss@umich.edu}{\nolinkurl{pschloss@umich.edu}}

\textsuperscript{1}Department of Microbiology and Immunology, University
of Michigan, Ann Arbor, MI\\
\textsuperscript{2}Department of Internal Medicine, Division of
Infectious Disease, University of Michigan, Ann Arbor, MI\\
\textsuperscript{3}Department of Family Medicine and Community Medicine,
Penn State Hershey Medical Center, Hershey, PA\\
\textsuperscript{4}Department of Internal Medicine, University of
Michigan, Ann Arbor, MI \textbackslash{}end\{center\}

>>>>

\vspace{25mm}

\begin{center}
Running Title: Human Microbiome and Colorectal Cancer

@@

Marc A Sze${^1}$, Nielson T Baxter${^2}$, Mack T Ruffin IV${^3}$, Mary AM Rogers${^2}$, and Patrick D Schloss${^1}$${^\dagger}$

@@

$\dagger$ To whom correspondence should be addressed: pschloss@umich.edu

$1$ Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI

$2$ Department of Internal Medicine, University of Michigan, Ann Arbor, MI

$3$ Department of Family Medicine and Community Medicine, Penn State Hershey Medical Center, Hershey, PA

\end{center}
